---
title: "Neuroecon Poster Figures"
output:
  html_document: default
  pdf_document: default
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(stringr)
library(plotly)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
options(scipen = 1, digits = 4, width = 500)
```

Lit review figure

```{r}

```

Bootstrapped reliabilities figure mirroring lit review figure
(most likely excludes DDM)

```{r}

```

Histogram of point estimates comparing distributions of survey vs. task measures

```{r}

```

Stats comparing reliabilities of surveys vs tasks

```{r}

```

Table for survey reliabilities by survey name

```{r}

```

Stats checking if item number makes a difference for reliability estimates for surveys

```{r}

```

Table for task reliabilities by task name

```{r}

```

Stats checking if item number makes a difference for reliability estimates for tasks

```{r}

```

Table for task reliabilities by cognitive construct

```{r}

```

Histogram of DDM vs. RT and accuracy measures

```{r}

```

Statistics comparing average reliabilities for DDM vs raw measures

```{r}

```

Note on metric for retest reliabilities
Scatter plots showing relationships between ICC, Pearson and Spearman

```{r}

```