---
title: 'SRO Retest Data Cleaning'
output:
github_document:
toc: yes
toc_float: yes
---

#################################
NOT USED
#################################

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
library(DT)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/reports', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

### Clean t1 data

The cleaning functions here are translated from the python pipeline to mimick the same procedure that was applied to the `meaningful_variables` in creating `meaningful_variables_clean`.

The original cleaning procedures include three steps:  
1. Removing outliers for each variable where outliers are defined as those who are greater than 2.5 IQR from median. **This step is skipped here because removing outliers from either dataset could lead to an unnecessary increase in missing data. Since we are interested in the average distance between two measures of a metric for a given subject instead of the distance between all these metrics this seemed appropriate.**  
2. Removing correlated variables *within* a task. In creating `meaningful_variables_clean` if variables for a given task correlated >.85 only one was kept. **This step is skipped here because we want to look at the reliability of as many variables as we can.**  
3. Log transforming variables with skew. In cleaning t1 data variables that had a |skew| > 1 were log transformed and those for which skew could not be removed successfully were dropped. **Here we transform all variables that have a |skew|>1 in t1 data but variables that are not successfully transformed (i.e. where the transformation has not decreased the skew below the threshold) will be listed and not dropped.**

```{r}
remove_outliers = function(data_column, quantile_range = 2.5){
  
  q_25 = quantile(data_column, na.rm=T)[2]
  q_50 = quantile(data_column, na.rm=T)[3]
  q_75 = quantile(data_column, na.rm=T)[4]
  
  lowlimit = q_50 - quantile_range*(q_75 - q_25)
  highlimit = q_50 + quantile_range*(q_75 - q_25)
  
  data_column = ifelse(data_column<lowlimit, NA, ifelse(data_column>highlimit, NA, data_column))
  
  return(data_column)
}

"%w/o%" <- function(x, y) x[!x %in% y]

pos_log <- function(column){
  col_min = min(column, na.rm=T)
  a = 1-col_min
  column = column+a
  return(log(column))
}

neg_log <- function(column){
  col_max = max(column, na.rm=T)
  column = col_max+1-column
  return(log(column))
}

transform_remove_skew = function(data, columns, threshold = 1, drop=FALSE){
  
  tmp = as.data.frame(apply(data[,columns],2,skew))
  names(tmp) = c("skew")
  tmp$dv = row.names(tmp)
  tmp = tmp %>% 
    filter(abs(skew)>threshold)
  
  skewed_variables = tmp$dv
  skew_subset = data[, skewed_variables]
  positive_subset = data[,tmp$dv[tmp$skew>0]]
  negative_subset = data[,tmp$dv[tmp$skew<0]]
  
  # transform variables
  # log transform for positive skew
  # positive_subset = log(positive_subset)
  # positive_subset = pos_log(positive_subset) #slight divergence from original code
  positive_subset = as.data.frame(apply(positive_subset, 2, pos_log))
  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
  names(successful_transforms) = c('skew')
  successful_transforms$dv = row.names(successful_transforms)
  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
  successful_transforms = successful_transforms$dv
  successful_transforms = positive_subset[,successful_transforms]
  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)
  
  cat(rep('*', 40))
  cat('\n')
  cat(paste0(length(names(positive_subset)) ,' data positively skewed data were transformed:'))
  cat('\n')
  cat(names(positive_subset), sep = '\n')
  cat(rep('*', 40))
  cat('\n')
  
  # replace transformed variables
  data = data[,-c(which(names(data) %in% names(positive_subset)))]
  
  if(drop == TRUE){
    names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
    cat(rep('*', 40))
    cat('\n')
    cat(paste0('Dropping ', length(dropped_vars) ,' positively skewed data that could not be transformed successfully:'))
    cat('\n')
    cat(dropped_vars, sep = '\n')
    cat(rep('*', 40))
    cat('\n')
    data = cbind(data, successful_transforms)
  }
  else{
    names(positive_subset) = paste0(names(positive_subset), '.logTr')
    cat(rep('*', 40))
    cat('\n')
    cat(paste0(length(dropped_vars) ,' positively skewed data could not be transformed successfully:'))
    cat('\n')
    cat(dropped_vars, sep = '\n')
    cat(rep('*', 40))
    cat('\n')
    data = cbind(data, positive_subset)
  }
  
  
  # reflected log transform for negative skew      
  negative_subset = as.data.frame(apply(negative_subset, 2, neg_log))
  successful_transforms = as.data.frame(apply(negative_subset, 2, skew))
  names(successful_transforms) = c('skew')
  successful_transforms$dv = row.names(successful_transforms)
  successful_transforms = successful_transforms %>% filter(abs(skew)<1)
  successful_transforms = successful_transforms$dv
  successful_transforms = negative_subset[,successful_transforms]
  dropped_vars = names(negative_subset) %w/o% names(successful_transforms)
  
  cat(rep('*', 40))
  cat('\n')
  cat(paste0(length(names(negative_subset)) ,' data negatively skewed data were transformed:'))
  cat('\n')
  cat(names(negative_subset), sep = '\n')
  cat(rep('*', 40))
  cat('\n')
  
  # replace transformed variables
  data = data[,-c(which(names(data) %in% names(negative_subset)))]
  if(drop == TRUE){
    names(successful_transforms) = paste0(names(successful_transforms), '.ReflogTr')
    cat(rep('*', 40))
    cat('\n')
    cat(paste0('Dropping ', length(dropped_vars) ,' negatively skewed data that could not be transformed successfully:'))
    cat('\n')
    cat(dropped_vars, sep = '\n')
    cat(rep('*', 40))
    cat('\n')
    data = cbind(data, successful_transforms)
  }
  else{
    names(negative_subset) = paste0(names(negative_subset), '.ReflogTr')
    cat(rep('*', 40))
    cat('\n')
    cat(paste0(length(dropped_vars) ,' negatively skewed data could not be transformed successfully:'))
    cat('\n')
    cat(dropped_vars, sep = '\n')
    cat(rep('*', 40))
    cat('\n')
    data = cbind(data, negative_subset)
  }
  
  return(data)
}
```

Clean t1 data on full sample without dropping any columns. Columns that are not transformed successfully are listed.

```{r warning=FALSE}
numeric_cols = c()

for(i in 1:length(names(test_data))){
  if(is.numeric(test_data[,i])){
    numeric_cols <- c(numeric_cols, names(test_data)[i])
  }
}

# clean_test_data = cbind(sub_id = test_data$sub_id, as.data.frame(apply(test_data[, -which(names(test_data) %in% c("sub_id"))], 2, remove_outliers)))

# clean_test_data = transform_remove_skew(clean_test_data, numeric_cols)
clean_test_data = transform_remove_skew(test_data, numeric_cols)
```

```{r echo=FALSE}
rm(i)
```

### Clean t2 data

Instead of applying the same functions applied to t1 data we check which variables are transformed in what way and transform the t2 data the same way. Again we are not removing outliers in the t2 or dropping variables if the skew is not removed successfully after transforming.

Get list of transformed variables and the sign of their skew
```{r}
logTr_vars = data.frame(grep('logTr', names(clean_test_data), value=T))
names(logTr_vars) = c('var')
logTr_vars$sign = ifelse(grepl(".ReflogTr",logTr_vars$var), 'negative', 'positive')
logTr_vars$var = gsub(".logTr|.ReflogTr", "", logTr_vars$var)
```

Transform the t2 columns the same way t1 columns were transformed.

```{r warning=FALSE}
clean_retest_data = retest_data

for(i in 1:length(names(clean_retest_data))){
  tmp_col = names(clean_retest_data)[i]
  if(tmp_col %in% logTr_vars$var){
    sign = logTr_vars$sign[which(tmp_col == logTr_vars$var)]
      if(sign == 'positive'){
        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
        clean_retest_data[,tmp_col] = pos_log(clean_retest_data[,tmp_col])
        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.logTr')
        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
        cat('\n')
      }
      else if(sign == 'negative'){
        clean_retest_data[,tmp_col] = neg_log(clean_retest_data[,tmp_col])
        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
        cat('\n')
      }
    }
}
```

```{r echo = FALSE}
rm(i, sign, tmp_col)
```

Check transformations are correct
```{r}
retest_logTr_vars = data.frame(grep('logTr', names(clean_retest_data), value=T))
names(retest_logTr_vars) = c('var')
retest_logTr_vars$sign = ifelse(grepl(".ReflogTr",retest_logTr_vars$var), 'negative', 'positive')
retest_logTr_vars$var = gsub(".logTr|.ReflogTr", "", retest_logTr_vars$var)
retest_logTr_vars = retest_logTr_vars %>% arrange(var)
logTr_vars = logTr_vars %>% arrange(var)
retest_logTr_vars == logTr_vars
```


```{r echo=FALSE}
rm(logTr_vars, retest_logTr_vars)
```

```{r}
# Switch df names
raw_retest_data = retest_data
raw_test_data = test_data
test_data = clean_test_data
retest_data = clean_retest_data
rm(clean_test_data, clean_retest_data)
```
